Open-Set Domain Adaptation through Self-Supervision

### 2022-01-22 Report/Paper_OpenSet.tex
Report - finished center loss section

\begin{figure}[!htbp]
  \centering
  %\begin{adjustbox}{minipage=\linewidth,scale=0.8}
  \begin{subfigure}[b]{0.4\columnwidth}
    \centering
    \includegraphics[width=\linewidth]{Figures/FlipRaw.png}
    \caption{Raw image}
    \label{fig:short-a}
  \end{subfigure}
  \begin{subfigure}[b]{0.4\columnwidth}
\centering
    \includegraphics[width=\linewidth]{Figures/FlipHoriz.png}
    \caption{Horizontally flipped}
    \label{fig:short-b}
  \end{subfigure}
%\end{adjustbox}
  \caption{Horizontal flipping of an image, adapted from \cite{Xu22019}.}
  \label{fig:centerloss}
\end{figure}

@@

\begin{figure*}[!htb]
  \centering
   \includegraphics[width=0.95\linewidth]{Figures/Jigsaw.png}
   \caption{Jigsaw puzzle self-supervised task method \cite{Carlucci2019}.}
   \label{fig:jigsaw}
\end{figure*}

@@

An ablation study was performed to select the most appropriate weight of the center loss contribution.

- describe each of the variations
- present results of the performance of the model and compare with the baseline for each of the variations

>>>>

\begin{figure}[!htbp]
  \centering
  %\begin{adjustbox}{minipage=\linewidth,scale=0.8}
  \begin{subfigure}[b]{0.4\columnwidth}
    \centering
    \includegraphics[width=\linewidth]{Figures/FlipRaw.jpg}
    \caption{Raw image}
    \label{fig:short-a}
  \end{subfigure}
\hspace{0.01\textwidth}
  \begin{subfigure}[b]{0.4\columnwidth}
\centering
    \includegraphics[width=\linewidth]{Figures/FlipHoriz.jpg}
    \caption{Horizontally flipped}
    \label{fig:short-b}
  \end{subfigure}
%\end{adjustbox}
  \caption{Horizontal flipping of an image, adapted from \cite{OfficeHome}.}
  \label{fig:horiz}
\end{figure}

@@

\begin{figure*}[!htbp]
  \centering
   \includegraphics[width=0.95\linewidth]{Figures/Jigsaw.png}
   \caption{Jigsaw puzzle self-supervised task method \cite{Carlucci2019}.}
   \label{fig:jigsaw}
\end{figure*}

@@

The center loss has been implemented during the first step of the model, and used to understand the effect of this loss on the separation phase.

An ablation study was performed to select the most appropriate weight ($\alpha_w$) of the center loss contribution. The initial weights considered were based on those reported by Bucci \etal \cite{Bucci2020} in their research on the Office-Home \cite{OfficeHome} and Office31 datasets \cite{Office31}. High values of $\alpha_w$ were found to give too much importance to the center loss at the expense of the soft max loss, and the model converged extremely slowly. For this reason the results analysed here consider only weight values lower or equal to $0.01$.

Table \ref{tab:center_loss} shows a comparison of the AUC values with and without the introduction of center loss, with $\alpha_1 = 10$ trained for 40 epochs. The inclusion of center loss was able to improve the accuracy for all domain configurations considered. It also improved the AUC metric for the second two domain configurations, however was detrimental in the first configuration. Due to the similarity of the results presented in \ref{tab:center_loss} the findings are inconclusive, and further investigations would be necessary to understand if the center loss could be used effectively in this scenario.

\begin{table}
	\centering
	\small
	\begin{tabular}{|l|c|c|c|c|}
		\hline
		 & & & \multicolumn{2}{c|}{\textbf{Weight  $\alpha_w$}} \\
		Domains & Metric & Standard & 0.001 & 0.01\\
		\hline
		\multirow{2}{*}{Art $\to$ Clipart}
		& AUC & \textbf{0.5590} & 0.5486 & 0.5302\\ 
		& Accuracy & 0.8988 & 0.9150 & 0.9150\\
		\hline
		\multirow{2}{*}{Product $\to$ Art}
		& AUC & 0.4997 & \textbf{0.5077} & 0.5023\\ 
		& Accuracy & 0.9513 & 0.9612 & 0.9631\\
		\hline
		\multirow{2}{*}{Art $\to$ RealWorld}
		& AUC & 0.4956 & \textbf{0.5000} & 0.4967\\ 
		& Accuracy & 0.8988 & 0.9128 & 0.9139\\
		\hline
	\end{tabular}
	\caption{Comparison of center loss model with standard model}
	\label{tab:center_loss}
\end{table}
